Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-30 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

>>>>

*Canopy trees seem more vulnerable to mortality from distinct disturbances, such as drought or heat waves, whereas  more buffered understory trees may be exposed to chronic stress that could negatively impact their  carbon balance (which already has less reserves; @niinemetsResponsesForestTrees2010].*
